---
title: "Final Viz"
subtitle: "Visualizing forest health impacts of various treatment options"
author: "Liv Hemond"
date: 2025-03-08
format: 
  html:
    code-fold: show
    toc: true
    embed-resources: true
editor: visual
theme: litera
execute: 
  eval: true
  echo: true
  message: false
  warning: false
---

## I. Setup

### i. Load libraries and data

```{r}
# ..........load libraries.........
library(tidyverse)
library(here)
library(paletteer)
library(scales)
library(showtext)
library(ggridges)

#................enable {showtext} for rendering.................
showtext_auto()
showtext_opts(dpi = 300)

# ........set color palette.........
conifer <- paletteer_d("calecopal::conifer", n = 5)
# subset individual colors from palette
treatments <- c("Combined Thinning and Prescribed Fire" = "#979A6BFF", 
                "Prescribed Fire" = "#CC7540FF", 
                "Mechanical Thinning" = "#39692FFF", 
                "Control" = "#765043FF")


# ..........load data files.........
# part A: stand density index
  # stand density index (SDI)
  sdi_data <- read_csv(here("data", "sdi_data.csv")) 

# part B: fire risk
  # ptorch
  ptorch_data <- read_csv(here("data", "ptorch_data.csv"))
  
# part C: stable live tree carbon
  # stable live tree carbon (STLC)
  stlc_data <- read_csv(here("data", "sltc_data.csv"))
```

### ii. Clean and wrangle data

#### A. Stand density index

```{r}
# stand density index
sdi_clean <- sdi_data %>% 
  # convert treatment and sdi_zone (competitive benchmark zones) to factors and set levels
  mutate(treatment = factor(treatment, 
                            levels = c("control", "burn", "mech", "mechburn"),
                            labels = c("Control", "Prescribed Fire", "Mechanical Thinning",
                                       "Combined Thinning and Prescribed Fire")),
         sdi_zone_long = factor(sdi_zone,
                                levels = c(">60", "35-60", "25-35", "<25"),
                                labels = c("Extremely High", "High", "Moderate", "Low"))) 
```

#### B. Fire risk

```{r}
# ptorch (probability of torching, aka severe fire)
ptorch_clean <- ptorch_data %>% 
  # convert treatment to factor and set levels
  mutate(treatment = factor(treatment, 
                            levels = c("mechburn", "burn", "mech", "control"),
                            labels = c("Combined Thinning and Prescribed Fire", 
                                       "Prescribed Fire", 
                                       "Mechanical Thinning", "Control")))
```


#### C. Stable live tree carbon

```{r}
# stable live tree carbon (pre and post fire)
stlc_clean <- stlc_data %>% 
  # convert treatment to factor and set levels
  mutate(treatment = factor(treatment, 
                            levels = c("mechburn", "burn", "mech", "control"),
                            labels = c("Combined Thinning and Prescribed Fire", "Prescribed Fire", 
                                       "Mechanical Thinning", "Control")))
```

## II. Visualizations

### A. Stand density index

Show the percentage of plots in each treatment that fall into the highest stand density index zone (indicating greater competition and chance of mortality)

```{r}
#| fig-width: 8
#| fig-height: 10

# Process the data to calculate % of plots, for that treatment, in each SDI zone
density_plot <- sdi_clean %>%
  
  # first, count number of plots in each treatment type and SDI benchmark zone
  group_by(treatment, sdi_zone_long) %>%
  summarize(count_treatment_zone = n()) %>%
  ungroup() %>% 
  
  # second, add the counts to get the total number of plots in each treatment type
  group_by(treatment) %>% 
  mutate(count_treatment = sum(count_treatment_zone),
         
         # third, divide the number of plots per SDI zone by the number of total plots for that treatment 
         pct_zone_per_treatment = count_treatment_zone/count_treatment) %>% 
  
  # filter to only extremely high density plots
  filter(sdi_zone_long == "Extremely High") %>% 
  
  # set up ggplot
  ggplot(aes(x = treatment, y = pct_zone_per_treatment, color = treatment)) +
  
  geom_point(size = 5) +
  
  geom_linerange(aes(ymin = 0, ymax = pct_zone_per_treatment), 
                 alpha = 0.5,
                 linewidth = 2) +

  # wrap long labels
  scale_x_discrete(labels = label_wrap(20)) +
  
  # add y axis limits
  scale_y_continuous(limits = c(0, 0.75)) +
  
  # add colors
  scale_color_manual(values = treatments) +
  
  # add title, subtitle, and y axis label
  labs(title = "Percent of Plots with Extremely High Density Forest",
       subtitle = "Almost 75% of control plots face overcrowding and increased mortality risk",
       caption = "Data from Stephens et al. 2023.",
       y = "Percent of Plots") +
  
  # add percent labels to each line
  geom_text(aes(label = scales::percent(pct_zone_per_treatment, 
                                        scale = 100,
                                        accuracy = 1)), 
            hjust = -0.35, 
            vjust = -0.35,
            size = 5) +
  
  # apply themeing
  theme(
    # remove legend
    legend.position = "none",
    # remove axis titles and axes themselves
    axis.title = element_blank(),
    panel.background = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    #adjust title, subtitle, axis text
    plot.title = element_text(face = "bold",
                              size = 16,
                              hjust = 0.5,
                              margin = margin(10, 0, 10, 0)),
    plot.subtitle = element_text(size = 14,
                                 hjust = 0.5,
                                 margin = margin(0, 0, 10, 0)),
    axis.text = element_text(size = 14),
    # adjust caption
    plot.caption = element_text(face = "italic", 
                                color = "#484848",
                                size = 11,
                                hjust = 1,
                                margin = margin(20, 0, 10, 0))
  )
density_plot
```


### B. Fire risk

Compare probability of torching (aka probability of severe fire) across treatments

```{r}
#| fig-width: 9
#| fig-height: 6

fire_plot <- ptorch_clean %>% 
  
  ggplot(aes(x = ptorch, y = treatment, fill = treatment)) +
  # create rideline plot with raincloud of points underneath. use quantile line to mark median value
  geom_density_ridges(aes(point_color = treatment),
                               scale = 0.8, alpha = 0.8,
                               rel_min_height = 0.02,
                               jittered_points = TRUE, 
                               quantile_lines = TRUE, 
                               linewidth = 0.8,
                               vline_width = 0.8, vline_color = "black",
                               point_size = 0.4, point_alpha = 0.6, 
                               position = "raincloud",
                               quantiles = 2) +
  
  # wrap long labels on y axis
  scale_y_discrete(labels = label_wrap(20)) +
  
  # apply fill colors
  scale_fill_manual(values = treatments) +
  
  # apply point colors
  scale_discrete_manual("point_color", values = treatments) +
  
  # add title and axis label
  labs(title = "Forest Restoration Reduces the Risk of Severe Wildfire",
       subtitle = "Control plots face much greater fire risk overall",
       caption = "Data from Stephens et al. 2023.",
       x = "Probability of Severe Wildfire") +
  # add percent labels
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  
  # add themeing
  theme_classic() +
  theme(
    # remove legend and y axis title
    legend.position = "none",
    axis.title.y = element_blank(),
    
    #adjust title, subtitle, axis text
    plot.title = element_text(face = "bold", 
                              size = 16,
                              hjust = 0,
                              margin = margin(10, 0, 10, 0)),
    plot.subtitle = element_text(size = 14,
                                 hjust = 0,
                                 margin = margin(0, 0, 15, 0)),
    axis.text = element_text(size = 12,
                             margin = margin(10, 0, 0, 0)),
    axis.title.x = element_text(size = 14,
                                margin = margin(15, 0, 0, 0)),
    
    # adjust caption
    plot.caption = element_text(face = "italic", 
                                color = "#484848",
                                size = 11,
                                hjust = 1,
                                margin = margin(20, 0, 10, 0))
    )
fire_plot
```

### C. Stable live tree carbon

Compare stable live tree carbon (that which is expected to survive after a wildfire event) with existing carbon stocks

```{r}
#| fig-width: 8
#| fig-height: 8

# first, calculate the mean stlc and mean existing carbon for each treatment type
carbon_plot <- stlc_clean %>% 
  group_by(treatment) %>% 
  summarize(mean_carbon_mgha = mean(carbon_mgha),
            mean_stable_ltc_mgha = mean(stable_ltc_mgha)) %>% 
  pivot_longer(mean_carbon_mgha:mean_stable_ltc_mgha,
               names_to = "carbon_type",
               values_to = "carbon_mgha") %>% 
  
  # now create slope chart
  ggplot(aes(x = carbon_type, y = carbon_mgha, color = treatment, group = treatment)) +
  # add vertical lines as background
  geom_vline(xintercept = 1, color = "lightgray", linetype = "dashed") +
  geom_vline(xintercept = 2, color = "lightgray", linetype = "dashed") +
  
  geom_point(size = 3) +
  # add lines connecting the points
  geom_line() +
  
  # add number labels to each line (showing carbon in mg/ha)
  geom_text(aes(label = round(carbon_mgha, 0)), 
            hjust = -0.2, 
            vjust = -0.2,
            size = 4.5) +
  
  # add annotations to label each line with the treatment group name
  annotate(
    geom = "text",
    x = 0.88, y = 228,
    size = 14 / .pt,
    label = "Control",
    color = "#765043FF") +
  annotate(
    geom = "text",
    x = 0.78, y = 170,
    size = 14 / .pt,
    label = "Prescribed Fire",
    color = "#CC7540FF") +
  annotate(
    geom = "text",
    x = 0.7, y = 164,
    size = 14 / .pt,
    label = "Mechanical Thinning",
    color = "#39692FFF") +
  annotate(
    geom = "text",
    x = 0.7, y = 126,
    size = 14 / .pt,
    label = "Combined Thinning\nand Prescribed Fire",
    color = "#979A6BFF") +
  
  # apply color palette based upon treatment
  scale_color_manual(values = treatments) +
  
  # change x axis labels
  scale_x_discrete(labels = c("Pre-Fire", "Post-Fire")) +
  
  labs(title = "Carbon Stocks in Mg/ha Before and After a Simulated Fire",
       subtitle = "Control plots risk losing the greatest amount of carbon from wildfires",
       caption = "Data from Stephens et al. 2023.") +

  theme(
    # remove legend, gridlines, axis lines, axis titles
    legend.position = "none",
    panel.background = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    #adjust title, subtitle, and axis text
    plot.title = element_text(face = "bold", 
                              size = 16,
                              hjust = 0.5,
                              margin = margin(10, 0, 10, 0)),
    plot.subtitle = element_text(size = 14,
                                 hjust = 0.5,
                                 margin = margin(0, 0, 20, 0)),
    axis.text.x = element_text(face = "bold",
                               size = 14,
                               margin = margin(10, 0, 0, 0)),
    # adjust caption
    plot.caption = element_text(face = "italic", 
                                color = "#484848",
                                size = 12,
                                hjust = 0.7,
                                margin = margin(20, 0, 10, 0))
  )
carbon_plot
```

## III. Save Plots

```{r}
# save plots
ggsave(
  filename = here::here("images", "fire-plot.pdf"),
  plot = fire_plot, 
  device = "pdf",
  width = 9, 
  height = 6,
  unit = "in"
)
```
